---
title: "EWS for Sizure Onset"
output: html_notebook
---
```{r, warning=FALSE}
library(ggplot2)
library(reshape2)
library(lubridate)
library(dplyr)
library(ROCR)
library(pROC)
#library(glmnet)
```


Initially, we will try to develop a method using the records from a single patient as an example.
We will be considering CHB24.
We will start by computing Variance and autocorrelation withing moving windows.
Since the temporal resolution is quite high, we use disjoint intervals; otherwise the computation might be too heavy.
The lowest frequency among commonly observed oscillations are the Delta waves with a frequency of (1-4)Hz.
As such, an interval length of 1 second should be long enough not to be dominated by the phase of a low-frequency wave.
The data is sampled at a rate of 256 samples per second.

```{r}
library(edf)
data <- read.edf("./EEG data/chb01/chb01_03_edited.edf")
#View(data)
```
In the following we define a function to compute running autocorrelation
```{r}
compute_running_autocorrelation <- function(signal, n_samples = 256){
  length_out <- length(signal)/n_samples
  rho <- numeric(length = length_out)
  #browser()
  for (i in (1:length_out)){
    rho[i] <- acf(signal[((i-1)*n_samples+1):(i*n_samples)], lag.max = 1, plot = FALSE)$acf[2]
  }
  rho
}
```
We test the above function
```{r}
test_data <- data$signal$FP1_F7$data
test_rho <- compute_running_autocorrelation(signal = test_data, n_samples = 256)
acf_object <- acf(test_data[1:256], lag.max = 1, plot = FALSE)$acf
```
In the following we define a function to compute running variance
```{r}
compute_running_variance <- function(signal, n_samples = 256){
  length_out <- length(signal)/n_samples
  var <- numeric(length = length_out)
  for (i in (1:length_out)){
    var[i] <- var(signal[((i-1)*n_samples+1):(i*n_samples)])
  }
  var
}
```
We test the above function
```{r}
test_var <- compute_running_variance(signal = test_data, n_samples = 256)
```

We now make a function to take list of EDF format and compute the running EWS on each signal and save them in a data frame.
The following is an outdated version of the function. The updated will be in the chunk immediately below.
```{r, eval = FALSE}
make_EWS <- function(data, n_samples = 256, var = TRUE, rho = TRUE){
  length_out <- length(data$signal$FP1_F7$t)/n_samples
  out <- list()
  if(rho == TRUE){
    rho_df <- data.frame(
      t = (1:length_out),
      FP1_F7_rho = compute_running_autocorrelation(signal = data$signal$FP1_F7$data),
      F7_T7_rho  = compute_running_autocorrelation(signal = data$signal$F7_T7$data),
      T7_P7_rho = compute_running_autocorrelation(signal = data$signal$T7_P7$data),
      P7_O1_rho = compute_running_autocorrelation(signal = data$signal$P7_O1$data),
      FP1_F3_rho = compute_running_autocorrelation(signal = data$signal$FP1_F3$data),
      F3_C3_rho = compute_running_autocorrelation(signal = data$signal$F3_C3$data),
      C3_P3_rho = compute_running_autocorrelation(signal = data$signal$C3_P3$data),
      P3_O1_rho = compute_running_autocorrelation(signal = data$signal$P3_O1$data),
      FP2_F4_rho = compute_running_autocorrelation(signal = data$signal$FP2_F4$data),
      F4_C4_rho = compute_running_autocorrelation(signal = data$signal$F4_C4$data),
      C4_P4_rho = compute_running_autocorrelation(signal = data$signal$C4_P4$data),
      P4_O2_rho = compute_running_autocorrelation(signal = data$signal$P4_O2$data),
      FP2_F8_rho = compute_running_autocorrelation(signal = data$signal$FP2_F8$data),
      F8_T8_rho = compute_running_autocorrelation(signal = data$signal$F8_T8$data),
      P8_O2_rho = compute_running_autocorrelation(signal = data$signal$P8_O2$data),
      FZ_CZ_rho = compute_running_autocorrelation(signal = data$signal$FZ_CZ$data),
      CZ_PZ_rho = compute_running_autocorrelation(signal = data$signal$CZ_PZ$data),
      P7_T7_rho = compute_running_autocorrelation(signal = data$signal$P7_T7$data),
      T7_FT9_rho = compute_running_autocorrelation(signal = data$signal$T7_FT9$data),
      FT9_FT10_rho = compute_running_autocorrelation(signal = data$signal$FT9_FT10$data),
      FT10_T8_rho = compute_running_autocorrelation(signal = data$signal$FT10_T8$data),
      T8_P8_rho = compute_running_autocorrelation(signal = data$signal$T8_P8$data)
    )
    out$rho <- rho_df
  }
  if(var == TRUE){
    var_df <- data.frame(
      t = (1:length_out),
      FP1_F7_var = compute_running_variance(signal = data$signal$FP1_F7$data),
      F7_T7_var  = compute_running_variance(signal = data$signal$F7_T7$data),
      T7_P7_var = compute_running_variance(signal = data$signal$T7_P7$data),
      P7_O1_var = compute_running_variance(signal = data$signal$P7_O1$data),
      FP1_F3_var = compute_running_variance(signal = data$signal$FP1_F3$data),
      F3_C3_var = compute_running_variance(signal = data$signal$F3_C3$data),
      C3_P3_var = compute_running_variance(signal = data$signal$C3_P3$data),
      P3_O1_var = compute_running_variance(signal = data$signal$P3_O1$data),
      FP2_F4_var = compute_running_variance(signal = data$signal$FP2_F4$data),
      F4_C4_var = compute_running_variance(signal = data$signal$F4_C4$data),
      C4_P4_var = compute_running_variance(signal = data$signal$C4_P4$data),
      P4_O2_var = compute_running_variance(signal = data$signal$P4_O2$data),
      FP2_F8_var = compute_running_variance(signal = data$signal$FP2_F8$data),
      F8_T8_var = compute_running_variance(signal = data$signal$F8_T8$data),
      P8_O2_var = compute_running_variance(signal = data$signal$P8_O2$data),
      FZ_CZ_var = compute_running_variance(signal = data$signal$FZ_CZ$data),
      CZ_PZ_var = compute_running_variance(signal = data$signal$CZ_PZ$data),
      P7_T7_var = compute_running_variance(signal = data$signal$P7_T7$data),
      T7_FT9_var = compute_running_variance(signal = data$signal$T7_FT9$data),
      FT9_FT10_var = compute_running_variance(signal = data$signal$FT9_FT10$data),
      FT10_T8_var = compute_running_variance(signal = data$signal$FT10_T8$data),
      T8_P8_var = compute_running_variance(signal = data$signal$T8_P8$data)
    )
    out$var <- var_df
  }
  out
}
```
Okay, let's test!
```{r, eval = FALSE} 
EWS_test <- make_EWS(data = data)
```

Let's make a plot: We'll need it anyways
```{r, eval = FALSE}
plot_data_var <- melt(EWS_test$var, id.vars = "t")
ggplot(data = plot_data_var, mapping = aes(x = t, y = value, colour = variable)) + geom_line()
```
```{r, eval = FALSE}
plot_data_rho <- melt(EWS_test$rho, id.vars = "t")
ggplot(data = plot_data_rho, mapping = aes(x = t, y = value, colour = variable)) + geom_line()
```
Below, we define the updated make_EWS function:
```{r}
make_EWS <- function(data, n_samples = 256, var = TRUE, rho = TRUE){
  length_out <- length(data$signal$FP1_F7$t)/n_samples
  if(rho == TRUE){
    rho_df <- data.frame(
      t = (1:length_out)*(n_samples/256),
      FP1_F7_rho = compute_running_autocorrelation(signal = data$signal$FP1_F7$data, n_samples = n_samples),
      F7_T7_rho  = compute_running_autocorrelation(signal = data$signal$F7_T7$data, n_samples = n_samples),
      T7_P7_rho = compute_running_autocorrelation(signal = data$signal$T7_P7$data, n_samples = n_samples),
      P7_O1_rho = compute_running_autocorrelation(signal = data$signal$P7_O1$data, n_samples = n_samples),
      FP1_F3_rho = compute_running_autocorrelation(signal = data$signal$FP1_F3$data, n_samples = n_samples),
      F3_C3_rho = compute_running_autocorrelation(signal = data$signal$F3_C3$data, n_samples = n_samples),
      C3_P3_rho = compute_running_autocorrelation(signal = data$signal$C3_P3$data, n_samples = n_samples),
      P3_O1_rho = compute_running_autocorrelation(signal = data$signal$P3_O1$data, n_samples = n_samples),
      FP2_F4_rho = compute_running_autocorrelation(signal = data$signal$FP2_F4$data, n_samples = n_samples),
      F4_C4_rho = compute_running_autocorrelation(signal = data$signal$F4_C4$data, n_samples = n_samples),
      C4_P4_rho = compute_running_autocorrelation(signal = data$signal$C4_P4$data, n_samples = n_samples),
      P4_O2_rho = compute_running_autocorrelation(signal = data$signal$P4_O2$data, n_samples = n_samples),
      FP2_F8_rho = compute_running_autocorrelation(signal = data$signal$FP2_F8$data, n_samples = n_samples),
      F8_T8_rho = compute_running_autocorrelation(signal = data$signal$F8_T8$data, n_samples = n_samples),
      P8_O2_rho = compute_running_autocorrelation(signal = data$signal$P8_O2$data, n_samples = n_samples),
      FZ_CZ_rho = compute_running_autocorrelation(signal = data$signal$FZ_CZ$data, n_samples = n_samples),
      CZ_PZ_rho = compute_running_autocorrelation(signal = data$signal$CZ_PZ$data, n_samples = n_samples),
      P7_T7_rho = compute_running_autocorrelation(signal = data$signal$P7_T7$data, n_samples = n_samples),
      T7_FT9_rho = compute_running_autocorrelation(signal = data$signal$T7_FT9$data, n_samples = n_samples),
      FT9_FT10_rho = compute_running_autocorrelation(signal = data$signal$FT9_FT10$data, n_samples = n_samples),
      FT10_T8_rho = compute_running_autocorrelation(signal = data$signal$FT10_T8$data, n_samples = n_samples),
      T8_P8_rho = compute_running_autocorrelation(signal = data$signal$T8_P8$data, n_samples = n_samples)
    )
  }
  if(var == TRUE){
    var_df <- data.frame(
      t = (1:length_out)*(n_samples/256),
      FP1_F7_var = compute_running_variance(signal = data$signal$FP1_F7$data, n_samples = n_samples),
      F7_T7_var  = compute_running_variance(signal = data$signal$F7_T7$data, n_samples = n_samples),
      T7_P7_var = compute_running_variance(signal = data$signal$T7_P7$data, n_samples = n_samples),
      P7_O1_var = compute_running_variance(signal = data$signal$P7_O1$data, n_samples = n_samples),
      FP1_F3_var = compute_running_variance(signal = data$signal$FP1_F3$data, n_samples = n_samples),
      F3_C3_var = compute_running_variance(signal = data$signal$F3_C3$data, n_samples = n_samples),
      C3_P3_var = compute_running_variance(signal = data$signal$C3_P3$data, n_samples = n_samples),
      P3_O1_var = compute_running_variance(signal = data$signal$P3_O1$data, n_samples = n_samples),
      FP2_F4_var = compute_running_variance(signal = data$signal$FP2_F4$data, n_samples = n_samples),
      F4_C4_var = compute_running_variance(signal = data$signal$F4_C4$data, n_samples = n_samples),
      C4_P4_var = compute_running_variance(signal = data$signal$C4_P4$data, n_samples = n_samples),
      P4_O2_var = compute_running_variance(signal = data$signal$P4_O2$data, n_samples = n_samples),
      FP2_F8_var = compute_running_variance(signal = data$signal$FP2_F8$data, n_samples = n_samples),
      F8_T8_var = compute_running_variance(signal = data$signal$F8_T8$data, n_samples = n_samples),
      P8_O2_var = compute_running_variance(signal = data$signal$P8_O2$data, n_samples = n_samples),
      FZ_CZ_var = compute_running_variance(signal = data$signal$FZ_CZ$data, n_samples = n_samples),
      CZ_PZ_var = compute_running_variance(signal = data$signal$CZ_PZ$data, n_samples = n_samples),
      P7_T7_var = compute_running_variance(signal = data$signal$P7_T7$data, n_samples = n_samples),
      T7_FT9_var = compute_running_variance(signal = data$signal$T7_FT9$data, n_samples = n_samples),
      FT9_FT10_var = compute_running_variance(signal = data$signal$FT9_FT10$data, n_samples = n_samples),
      FT10_T8_var = compute_running_variance(signal = data$signal$FT10_T8$data, n_samples = n_samples),
      T8_P8_var = compute_running_variance(signal = data$signal$T8_P8$data, n_samples = n_samples)
    )
  }
  out <- merge.data.frame(rho_df, var_df)
  out
}
```

```{r, eval = FALSE} 
EWS_test <- make_EWS(data = data, n_samples = 512)
```


We continue and turn our attention to reading each record of patient 24 and combining them into a single time series.
```{r, eval = FALSE}
data_files_24 <- list.files(path = "./EEG data/chb24")
data_files_24 <- data_files_24[1:22]
EWS_matrices <- list()
rf_date <- read.edf("./EEG data/chb24/chb24_01.edf")$header.global$startdate
rf_date <- as.Date(rf_date, format = "%d.%m.%y")
rf_time <- read.edf("./EEG data/chb24/chb24_01.edf")$header.global$starttime
starttime <- paste(rf_date, rf_time)
starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
for (filename in data_files_24){
  data <- read.edf(paste("./EEG data/chb24/", filename, sep = ""))
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
  
  #Computation
  EWS_matrix <- make_EWS(data, n_samples = 512)
  EWS_matrix$t <- EWS_matrix$t + starttime
  EWS_matrices[[filename]] <- EWS_matrix
}

saveRDS(EWS_matrices, file = "EWS_matrices_patient_24")
```

```{r}
EWS_matrices <- readRDS(file = "EWS_matrices_patient_24")
```

```{r}
EWS_24 <- bind_rows(EWS_matrices)
#plot(EWS_24$t)
#plot(diff(EWS_24$t))
EWS_24$is_preictal <- 0
```


We now enter the start and end times of seizures manually.
```{r}
seizure_no <- 1:16
start <- c(480, 2451, 231, 2883, 1088, 1411, 1745, 1229, 38, 1745, 3527, 3288, 1939, 3552, 2515, 2804)
end <- c(505,2476, 260, 2908, 1120, 1438, 1764, 1253, 60, 1764, 3597, 3304, 1966, 3569, 3581, 2872)
seizure_times <- data.frame(seizure_no, start, end)
```
We add the start and end times from the respective files to align with canonical time rather than time fromr record start.
```{r}
#File 1
  data <- read.edf("./EEG data/chb24/chb24_01.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[1:2, 2:3] <- seizure_times[1:2, 2:3] + starttime
```
```{r}
#File 3
  data <- read.edf("./EEG data/chb24/chb24_03.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[3:4, 2:3] <- seizure_times[3:4, 2:3] + starttime
```
```{r}
#File 4
  data <- read.edf("./EEG data/chb24/chb24_03.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[5:7, 2:3] <- seizure_times[5:7, 2:3] + starttime
```
```{r}
#File 6
  data <- read.edf("./EEG data/chb24/chb24_06.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[8, 2:3] <- seizure_times[8, 2:3] + starttime
```
```{r}
#File 7
  data <- read.edf("./EEG data/chb24/chb24_07.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[9, 2:3] <- seizure_times[9, 2:3] + starttime
```
```{r}
#File 9
  data <- read.edf("./EEG data/chb24/chb24_09.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[10, 2:3] <- seizure_times[10, 2:3] + starttime
```
```{r}
#File 11
  data <- read.edf("./EEG data/chb24/chb24_11.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[11, 2:3] <- seizure_times[11, 2:3] + starttime
```
```{r}
#File 13
  data <- read.edf("./EEG data/chb24/chb24_13.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[12, 2:3] <- seizure_times[12, 2:3] + starttime
```
```{r}
#File 14
  data <- read.edf("./EEG data/chb24/chb24_14.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[13, 2:3] <- seizure_times[13, 2:3] + starttime
```
```{r}
#File 15
  data <- read.edf("./EEG data/chb24/chb24_15.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[14, 2:3] <- seizure_times[14, 2:3] + starttime
```
```{r}
#File 17
  data <- read.edf("./EEG data/chb24/chb24_17.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[15, 2:3] <- seizure_times[15, 2:3] + starttime
```
```{r}
#File 21
  data <- read.edf("./EEG data/chb24/chb24_21.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[16, 2:3] <- seizure_times[16, 2:3] + starttime
```

We remove the data from ictal periods,
```{r}
for (i in (1:16)){
  EWS_24 <- EWS_24[(EWS_24$t <= seizure_times[i,2]) | (EWS_24$t > (seizure_times[i,3])+1), ]
}
```

We label observations within the 120s preceding seizure onsets as preictal.
```{r}
for (i in (1:16)){
  preictal <- (EWS_24$t <= seizure_times[i,2]) & (EWS_24$t > (seizure_times[i,2] - 120))
  EWS_24$is_preictal[preictal] <- 1
}
```
We remove NaN's from the data
```{r}
NAs <- which(is.na(EWS_24), arr.ind = TRUE)
no_NAs <- dim(NAs)[1]
for(i in (1:no_NAs)){
  EWS_24[NAs[i,1],NAs[i,2]] <- EWS_24[NAs[i,1]-1, NAs[i,2]-1]
}
```


Finally, we have our preprocessed dataset that we will use to do prediction.
We will do weighted logistic regression, and since we wish to test predictive performance, we save roughly third of the data as testing data. The data from record 13 and on will be labelled test data while record 1 through 12 will be labelled training data.
```{r}
#File 13
  data <- read.edf("./EEG data/chb24/chb24_13.edf")
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)

training_data <- EWS_24[(EWS_24$t) < starttime,]
test_data <- EWS_24[(EWS_24$t) >= starttime,]
```

Fitting a non-penalized model using GLM
```{r}
model <- glm(formula = is_preictal ~ . -t, family = binomial(link = "logit"), data = training_data)
summary(model)
```
Assessing the fit
```{r}
fitted_values <- model$fitted.values
fitted_values <- ifelse(fitted_values > 0.2,1,0)
misClasificError_fit <- mean(fitted_values != training_data$is_preictal)
misClasificError_fit
plot(fitted_values)
plot(training_data$is_preictal)
```
Assesing performance
```{r}
predicted_results <- predict(model, newdata = test_data, type = "response")
predicted_results <- ifelse(predicted_results > 0.2,1,0)
misClasificError <- mean(predicted_results != test_data$is_preictal)
misClasificError
sum(predicted_results)
plot(predicted_results)
plot(test_data$is_preictal)
```
Despite this result not being abysmal on its face, it comes largely from making most predictions negative.
Lets compute sensitivity and specificity
```{r}
table <- table(Predictions = predicted_results, TrueLabels = test_data$is_preictal)
table
sensitivity <- table[2,2]/(table[2,2] + table[1,2])
sensitivity
specificity <- table[1,1]/(table[1,1] + table[2,1])
specificity
```


Let's make a ROC-curve.
```{r}
predicted_results <- predict(model, newdata = test_data, type = "response")
pr <- prediction(predicted_results, test_data$is_preictal)
prf <- performance(pr, measure = "tpr", x.measure = "fpr")
plot(prf)
auc <- performance(pr, measure = "auc")
auc <- auc@y.values[[1]]
auc
```
Let's make a prettier one
```{r}
rocobj <- roc(test_data$is_preictal, predicted_results)
auc <- round(auc(test_data$is_preictal, predicted_results), 4)
ggroc(rocobj) + ggtitle(paste0('ROC Curve ', '(AUC = ', auc, ')'))
    theme(aspect.ratio = 1)
```



We attempted to fit a model using penalization, but did not have good results.
Perhaps data should be normalized first.
```{r, eval = FALSE}
x <- model.matrix(is_preictal~.-t, training_data)
y <- training_data$is_preictal
cv_ridge <- cv.glmnet(x, y, alpha = 0, family = "binomial")
model <- glmnet(x, y, alpha = 0, family = "binomial", lambda = cv_ridge$lambda.min)
coef(model)
fitted_values <- predict(model, newx = x)
x_test <- model.matrix(is_preictal~.-t, test_data)
probabilities <- predict(model, newx = x_test)
predicted_classes <- ifelse(probabilities > -5, 1, 0)
sum(predicted_classes)
```
That does not work at all for me.


Dorsa et al propose a postprocessing method to increase performance: group observations in batches of 10.
Then, if all observations within a group are positive, issue a warning.
This reduces warnings from spurious swings, and lets us ramp up the sensitivity of our method.
We attempted to omplement this, but we cannot get a result.
```{r, eval = FALSE}
trigger_alarm <- numeric(length = (dim(training_data))[1] - 1)
for (i in (1:(length(trigger_alarm)))){
  data <- fitted_values[i:(i+1)]
  if (mean(data, na.rm = TRUE) > 0.75){
    trigger_alarm <- 1
  }
}
sum(trigger_alarm, na.rm = T)
```

