---
title: "EWS for Sizure Onset"
output: html_notebook
---
```{r, warning=FALSE}
library(ggplot2)
library(reshape2)
library(lubridate)
library(dplyr)
```


Initially, we will try to develop a method using the records from a single patient as an example.
We will be considering CHB24.
We will start by computing Variance and autocorrelation withing moving windows.
Since the temporal resolution is quite high, we use disjoint intervals; otherwise the computation might be too heavy.
The lowest frequency among commonly observed oscillations are the Delta waves with a frequency of (1-4)Hz.
As such, an interval length of 1 second should be long enough not to be dominated by the phase of a low-frequency wave.
The data is sampled at a rate of 256 samples per second.

```{r}
library(edf)
data <- read.edf("./EEG data/chb01/chb01_03_edited.edf")
#View(data)
```
In the following we define a function to compute running autocorrelation
```{r}
compute_running_autocorrelation <- function(signal, n_samples = 256){
  length_out <- length(signal)/n_samples
  rho <- numeric(length = length_out)
  #browser()
  for (i in (1:length_out)){
    rho[i] <- acf(signal[((i-1)*n_samples+1):(i*n_samples)], lag.max = 1, plot = FALSE)$acf[2]
  }
  rho
}
```
We test the above function
```{r}
test_data <- data$signal$FP1_F7$data
test_rho <- compute_running_autocorrelation(signal = test_data, n_samples = 256)
acf_object <- acf(test_data[1:256], lag.max = 1, plot = FALSE)$acf
```
In the following we define a function to compute running variance
```{r}
compute_running_variance <- function(signal, n_samples = 256){
  length_out <- length(signal)/n_samples
  var <- numeric(length = length_out)
  for (i in (1:length_out)){
    var[i] <- var(signal[((i-1)*n_samples+1):(i*n_samples)])
  }
  var
}
```
We test the above function
```{r}
test_var <- compute_running_variance(signal = test_data, n_samples = 256)
```

We now make a function to take list of EDF format and compute the running EWS on each signal and save them in a data frame.
The following is an outdated version of the function. The updated will be in the chunk immediately below.
```{r, eval = FALSE}
make_EWS <- function(data, n_samples = 256, var = TRUE, rho = TRUE){
  length_out <- length(data$signal$FP1_F7$t)/n_samples
  out <- list()
  if(rho == TRUE){
    rho_df <- data.frame(
      t = (1:length_out),
      FP1_F7_rho = compute_running_autocorrelation(signal = data$signal$FP1_F7$data),
      F7_T7_rho  = compute_running_autocorrelation(signal = data$signal$F7_T7$data),
      T7_P7_rho = compute_running_autocorrelation(signal = data$signal$T7_P7$data),
      P7_O1_rho = compute_running_autocorrelation(signal = data$signal$P7_O1$data),
      FP1_F3_rho = compute_running_autocorrelation(signal = data$signal$FP1_F3$data),
      F3_C3_rho = compute_running_autocorrelation(signal = data$signal$F3_C3$data),
      C3_P3_rho = compute_running_autocorrelation(signal = data$signal$C3_P3$data),
      P3_O1_rho = compute_running_autocorrelation(signal = data$signal$P3_O1$data),
      FP2_F4_rho = compute_running_autocorrelation(signal = data$signal$FP2_F4$data),
      F4_C4_rho = compute_running_autocorrelation(signal = data$signal$F4_C4$data),
      C4_P4_rho = compute_running_autocorrelation(signal = data$signal$C4_P4$data),
      P4_O2_rho = compute_running_autocorrelation(signal = data$signal$P4_O2$data),
      FP2_F8_rho = compute_running_autocorrelation(signal = data$signal$FP2_F8$data),
      F8_T8_rho = compute_running_autocorrelation(signal = data$signal$F8_T8$data),
      P8_O2_rho = compute_running_autocorrelation(signal = data$signal$P8_O2$data),
      FZ_CZ_rho = compute_running_autocorrelation(signal = data$signal$FZ_CZ$data),
      CZ_PZ_rho = compute_running_autocorrelation(signal = data$signal$CZ_PZ$data),
      P7_T7_rho = compute_running_autocorrelation(signal = data$signal$P7_T7$data),
      T7_FT9_rho = compute_running_autocorrelation(signal = data$signal$T7_FT9$data),
      FT9_FT10_rho = compute_running_autocorrelation(signal = data$signal$FT9_FT10$data),
      FT10_T8_rho = compute_running_autocorrelation(signal = data$signal$FT10_T8$data),
      T8_P8_rho = compute_running_autocorrelation(signal = data$signal$T8_P8$data)
    )
    out$rho <- rho_df
  }
  if(var == TRUE){
    var_df <- data.frame(
      t = (1:length_out),
      FP1_F7_var = compute_running_variance(signal = data$signal$FP1_F7$data),
      F7_T7_var  = compute_running_variance(signal = data$signal$F7_T7$data),
      T7_P7_var = compute_running_variance(signal = data$signal$T7_P7$data),
      P7_O1_var = compute_running_variance(signal = data$signal$P7_O1$data),
      FP1_F3_var = compute_running_variance(signal = data$signal$FP1_F3$data),
      F3_C3_var = compute_running_variance(signal = data$signal$F3_C3$data),
      C3_P3_var = compute_running_variance(signal = data$signal$C3_P3$data),
      P3_O1_var = compute_running_variance(signal = data$signal$P3_O1$data),
      FP2_F4_var = compute_running_variance(signal = data$signal$FP2_F4$data),
      F4_C4_var = compute_running_variance(signal = data$signal$F4_C4$data),
      C4_P4_var = compute_running_variance(signal = data$signal$C4_P4$data),
      P4_O2_var = compute_running_variance(signal = data$signal$P4_O2$data),
      FP2_F8_var = compute_running_variance(signal = data$signal$FP2_F8$data),
      F8_T8_var = compute_running_variance(signal = data$signal$F8_T8$data),
      P8_O2_var = compute_running_variance(signal = data$signal$P8_O2$data),
      FZ_CZ_var = compute_running_variance(signal = data$signal$FZ_CZ$data),
      CZ_PZ_var = compute_running_variance(signal = data$signal$CZ_PZ$data),
      P7_T7_var = compute_running_variance(signal = data$signal$P7_T7$data),
      T7_FT9_var = compute_running_variance(signal = data$signal$T7_FT9$data),
      FT9_FT10_var = compute_running_variance(signal = data$signal$FT9_FT10$data),
      FT10_T8_var = compute_running_variance(signal = data$signal$FT10_T8$data),
      T8_P8_var = compute_running_variance(signal = data$signal$T8_P8$data)
    )
    out$var <- var_df
  }
  out
}
```
Okay, let's test!
```{r, eval = FALSE} 
EWS_test <- make_EWS(data = data)
```

Let's make a plot: We'll need it anyways
```{r, eval = FALSE}
plot_data_var <- melt(EWS_test$var, id.vars = "t")
ggplot(data = plot_data_var, mapping = aes(x = t, y = value, colour = variable)) + geom_line()
```
```{r}
plot_data_rho <- melt(EWS_test$rho, id.vars = "t")
ggplot(data = plot_data_rho, mapping = aes(x = t, y = value, colour = variable)) + geom_line()
```
Below, we define the updated make_EWS function:
```{r}
make_EWS <- function(data, n_samples = 256, var = TRUE, rho = TRUE){
  length_out <- length(data$signal$FP1_F7$t)/n_samples
  if(rho == TRUE){
    rho_df <- data.frame(
      t = (1:length_out)*(n_samples/256),
      FP1_F7_rho = compute_running_autocorrelation(signal = data$signal$FP1_F7$data, n_samples = n_samples),
      F7_T7_rho  = compute_running_autocorrelation(signal = data$signal$F7_T7$data, n_samples = n_samples),
      T7_P7_rho = compute_running_autocorrelation(signal = data$signal$T7_P7$data, n_samples = n_samples),
      P7_O1_rho = compute_running_autocorrelation(signal = data$signal$P7_O1$data, n_samples = n_samples),
      FP1_F3_rho = compute_running_autocorrelation(signal = data$signal$FP1_F3$data, n_samples = n_samples),
      F3_C3_rho = compute_running_autocorrelation(signal = data$signal$F3_C3$data, n_samples = n_samples),
      C3_P3_rho = compute_running_autocorrelation(signal = data$signal$C3_P3$data, n_samples = n_samples),
      P3_O1_rho = compute_running_autocorrelation(signal = data$signal$P3_O1$data, n_samples = n_samples),
      FP2_F4_rho = compute_running_autocorrelation(signal = data$signal$FP2_F4$data, n_samples = n_samples),
      F4_C4_rho = compute_running_autocorrelation(signal = data$signal$F4_C4$data, n_samples = n_samples),
      C4_P4_rho = compute_running_autocorrelation(signal = data$signal$C4_P4$data, n_samples = n_samples),
      P4_O2_rho = compute_running_autocorrelation(signal = data$signal$P4_O2$data, n_samples = n_samples),
      FP2_F8_rho = compute_running_autocorrelation(signal = data$signal$FP2_F8$data, n_samples = n_samples),
      F8_T8_rho = compute_running_autocorrelation(signal = data$signal$F8_T8$data, n_samples = n_samples),
      P8_O2_rho = compute_running_autocorrelation(signal = data$signal$P8_O2$data, n_samples = n_samples),
      FZ_CZ_rho = compute_running_autocorrelation(signal = data$signal$FZ_CZ$data, n_samples = n_samples),
      CZ_PZ_rho = compute_running_autocorrelation(signal = data$signal$CZ_PZ$data, n_samples = n_samples),
      P7_T7_rho = compute_running_autocorrelation(signal = data$signal$P7_T7$data, n_samples = n_samples),
      T7_FT9_rho = compute_running_autocorrelation(signal = data$signal$T7_FT9$data, n_samples = n_samples),
      FT9_FT10_rho = compute_running_autocorrelation(signal = data$signal$FT9_FT10$data, n_samples = n_samples),
      FT10_T8_rho = compute_running_autocorrelation(signal = data$signal$FT10_T8$data, n_samples = n_samples),
      T8_P8_rho = compute_running_autocorrelation(signal = data$signal$T8_P8$data, n_samples = n_samples)
    )
  }
  if(var == TRUE){
    var_df <- data.frame(
      t = (1:length_out)*(n_samples/256),
      FP1_F7_var = compute_running_variance(signal = data$signal$FP1_F7$data, n_samples = n_samples),
      F7_T7_var  = compute_running_variance(signal = data$signal$F7_T7$data, n_samples = n_samples),
      T7_P7_var = compute_running_variance(signal = data$signal$T7_P7$data, n_samples = n_samples),
      P7_O1_var = compute_running_variance(signal = data$signal$P7_O1$data, n_samples = n_samples),
      FP1_F3_var = compute_running_variance(signal = data$signal$FP1_F3$data, n_samples = n_samples),
      F3_C3_var = compute_running_variance(signal = data$signal$F3_C3$data, n_samples = n_samples),
      C3_P3_var = compute_running_variance(signal = data$signal$C3_P3$data, n_samples = n_samples),
      P3_O1_var = compute_running_variance(signal = data$signal$P3_O1$data, n_samples = n_samples),
      FP2_F4_var = compute_running_variance(signal = data$signal$FP2_F4$data, n_samples = n_samples),
      F4_C4_var = compute_running_variance(signal = data$signal$F4_C4$data, n_samples = n_samples),
      C4_P4_var = compute_running_variance(signal = data$signal$C4_P4$data, n_samples = n_samples),
      P4_O2_var = compute_running_variance(signal = data$signal$P4_O2$data, n_samples = n_samples),
      FP2_F8_var = compute_running_variance(signal = data$signal$FP2_F8$data, n_samples = n_samples),
      F8_T8_var = compute_running_variance(signal = data$signal$F8_T8$data, n_samples = n_samples),
      P8_O2_var = compute_running_variance(signal = data$signal$P8_O2$data, n_samples = n_samples),
      FZ_CZ_var = compute_running_variance(signal = data$signal$FZ_CZ$data, n_samples = n_samples),
      CZ_PZ_var = compute_running_variance(signal = data$signal$CZ_PZ$data, n_samples = n_samples),
      P7_T7_var = compute_running_variance(signal = data$signal$P7_T7$data, n_samples = n_samples),
      T7_FT9_var = compute_running_variance(signal = data$signal$T7_FT9$data, n_samples = n_samples),
      FT9_FT10_var = compute_running_variance(signal = data$signal$FT9_FT10$data, n_samples = n_samples),
      FT10_T8_var = compute_running_variance(signal = data$signal$FT10_T8$data, n_samples = n_samples),
      T8_P8_var = compute_running_variance(signal = data$signal$T8_P8$data, n_samples = n_samples)
    )
  }
  out <- merge.data.frame(rho_df, var_df)
  out
}
```

```{r, eval = FALSE} 
EWS_test <- make_EWS(data = data, n_samples = 512)
```


We continue and turn our attention to reading each record of patient 24 and combining them into a single time series.
```{r, eval = FALSE}
data_files_24 <- list.files(path = "./EEG data/chb24")
data_files_24 <- data_files_24[1:22]
EWS_matrices <- list()
rf_date <- read.edf("./EEG data/chb24/chb24_01.edf")$header.global$startdate
rf_date <- as.Date(rf_date, format = "%d.%m.%y")
rf_time <- read.edf("./EEG data/chb24/chb24_01.edf")$header.global$starttime
starttime <- paste(rf_date, rf_time)
starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
for (filename in data_files_24){
  data <- read.edf(paste("./EEG data/chb24/", filename, sep = ""))
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
  
  #Computation
  EWS_matrix <- make_EWS(data, n_samples = 512)
  EWS_matrix$t <- EWS_matrix$t + starttime
  EWS_matrices[[filename]] <- EWS_matrix
}

saveRDS(EWS_matrices, file = "EWS_matrices_patient_24")
```

```{r}
EWS_matrices <- readRDS(file = "EWS_matrices_patient_24")
```

```{r}
EWS_24 <- bind_rows(EWS_matrices)
#plot(EWS_24$t)
#plot(diff(EWS_24$t))
EWS_24$is_preictal <- 0
```

We now enter the start and end times of seizures manually.
```{r}
seizure_no <- 1:16
start <- c(480, 2451, 231, 2883, 1088, 1411, 1745, 1229, 38, 1745, 3527, 3288, 1939, 3552, 2515, 2804)
end <- c(505,2476, 260, 2908, 1120, 1438, 1764, 1253, 60, 1764, 3597, 3304, 1966, 3569, 3581, 2872)
seizure_times <- data.frame(seizure_no, start, end)
```
We add the start and end times from the respective files to align with canonical time rather than time fromr record start.
```{r}
#File 1
  data <- read.edf("./EEG data/chb24/chb24_01.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[1:2, 2:3] <- seizure_times[1:2, 2:3] + starttime
```
```{r}
#File 3
  data <- read.edf("./EEG data/chb24/chb24_03.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[3:4, 2:3] <- seizure_times[3:4, 2:3] + starttime
```
```{r}
#File 4
  data <- read.edf("./EEG data/chb24/chb24_03.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[5:7, 2:3] <- seizure_times[5:7, 2:3] + starttime
```
```{r}
#File 6
  data <- read.edf("./EEG data/chb24/chb24_06.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[8, 2:3] <- seizure_times[8, 2:3] + starttime
```
```{r}
#File 7
  data <- read.edf("./EEG data/chb24/chb24_07.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[9, 2:3] <- seizure_times[9, 2:3] + starttime
```
```{r}
#File 9
  data <- read.edf("./EEG data/chb24/chb24_09.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[10, 2:3] <- seizure_times[10, 2:3] + starttime
```
```{r}
#File 11
  data <- read.edf("./EEG data/chb24/chb24_11.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[11, 2:3] <- seizure_times[11, 2:3] + starttime
```
```{r}
#File 13
  data <- read.edf("./EEG data/chb24/chb24_13.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[12, 2:3] <- seizure_times[12, 2:3] + starttime
```
```{r}
#File 14
  data <- read.edf("./EEG data/chb24/chb24_14.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[13, 2:3] <- seizure_times[13, 2:3] + starttime
```
```{r}
#File 15
  data <- read.edf("./EEG data/chb24/chb24_15.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[14, 2:3] <- seizure_times[14, 2:3] + starttime
```
```{r}
#File 17
  data <- read.edf("./EEG data/chb24/chb24_17.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[15, 2:3] <- seizure_times[15, 2:3] + starttime
```
```{r}
#File 21
  data <- read.edf("./EEG data/chb24/chb24_21.edf")
  
  #Timing
  rf_date <- data$header.global$startdate
  rf_time <- data$header.global$starttime
  starttime <- paste(rf_date, rf_time)
  starttime <- as.POSIXct(starttime, format = "%d.%m.%y %H.%M.%S")
  starttime <- as.numeric(starttime)
seizure_times[16, 2:3] <- seizure_times[16, 2:3] + starttime
```

We remove the data from ictal periods,
```{r}
for (i in (1:16)){
  EWS_24 <- EWS_24[(EWS_24$t <= seizure_times[i,2]) | (EWS_24$t > (seizure_times[i,3])+1), ]
}
```

We label observations within the 120s preceding seizure onsets as preictal.
```{r}
for (i in (1:16)){
  preictal <- (EWS_24$t <= seizure_times[i,2]) & (EWS_24$t > (seizure_times[i,2] - 120))
  EWS_24$is_preictal[preictal] <- 1
}
```


